\chapter{Preposition.}

\textsc{Prepositions}, so called because they are commonly \emph{put
  before} the words to which they are applied, serve to connect words
with one another, and to show the relation between them.

One great Use of Prepositions in English is to express those relations,
which in some languages are chiefly marked by Cases, or the different
endings of the Noun.

Most prepositions originally denoted the relation of Place, and have
been thence transferred to denote by similitude other relations. Thus,
\tl{out}, \tl{in}, \tl{through}, \tl{under}, \tl{by}, \tl{to},
\tl{from}, \tl{of}, \&c. \tl{Of} is much the same with \tl{from}; ``ask
\tl{of} me,'' that is, \tl{from} me: ``made \tl{of} wood;'' ``Son
\tl{of} Philip;'' that is, sprung \tl{from} him. \tl{For}, in its
primary sense, is \tl{pro}, \tl{loco alterius}, in the \tl{stead}, or
\tl{place}, of another. The notion of Place is very obvious in all the
rest.\footnote{The Particle \tl{a} before Participles, in the phrases
  \tl{a} coming, \tl{a} going, \tl{a} walking, \tl{a} shooting, \&c.;
  and before Nouns, as \tl{a}-bed, \tl{a}-board, \tl{a}-shore,
  \tl{a}-foot, \&c.; seems to be a true and genuine Preposition, a
  little disguised by familiar use and quick pronunciation. Dr. Wallis
  supposes it to be the preposition \tl{at}. I rather think it is the
  Preposition \tl{on}; the sense of which answers better to the
  intention of those expressions. \tl{At} has relation chiefly to
  \emph{place}: \tl{on} has a more general relation, and may be applied
  to \emph{action}, and many other things, as well as \emph{place}. ``I
  was \tl{on} coming, \tl{on} going,'' \&c.; that is, employed
  \emph{upon} that particular \emph{action}: so likewise those other
  phrases above-mentioned, \tl{a}-bed, \&c. exactly answer to \tl{on}
  bed, \tl{on} board, \tl{on} shore, \tl{on} foot. Dr. Bentley plainly
  supposed \tl{a} to be the same with \tl{on}; as appears from the
  following passage: ``He would have a learned University make
  Barbarisms \tl{a} purpose.'' Dissert. on Phalaris, p. 223. ``The
  depths \tl{on} trembling fell.'' J.\ Hopkins, Ps. lxxvii. 16. That is,
  as we now say in common discourse, ``they fell \tl{a} trembling.'' And
  the Preposition \tl{on} has manifestly deviated into \tl{a} in other
  instances: thus the Saxon compounded Prepositions \tl{on}gean,
  \tl{on}mang, \tl{on}butan, are became in English, by the rapidity of
  pronunciation, \tl{a}gainst, \tl{a}mong, \tl{a}bout; and what is in
  the Saxon Gospel, ``Ic wylle gan \tl{on} fixoth,'' is in the English
  Translation, ``I go \tl{a} fishing.'' John xxi. 3. Much in the same
  manner, John \tl{of} Nokes, and John \tl{of} Stiles, by very frequent
  and familiar use, became John \tl{a} Nokes, and John \tl{a} Stiles:
  and one \tl{of the} clock, or rather \tl{on the} clock, is written,
  one \tl{o}'clock, but pronounced, one \tl{a} clock. The phrases with
  \tl{a} before Participles are out of use in the solemn style; but
  still prevail in familiar discourse. They are established by long
  usage, and good authority: and there seems to be no reason, why they
  should be utterly rejected.}

Prepositions are also prefixed to words in such a manner, as to coalesce
with them, and to become a part of them. Prepositions, standing by
themselves in Construction, are put before Nouns and Pronouns; and
sometimes after Verbs; but in this sort of Composition they are chiefly
prefixed to Verbs: as, \tl{to outgo}, \tl{to overcome}, \tl{to
  undervalue}. There are also certain Particles, which are thus employed
in Composition of words, yet cannot stand by themselves in Construction:
as, \tl{a}, \tl{be}, \tl{con}, \tl{mis}, \&c.; in \tl{abide},
\tl{bedeck}, \tl{conjoin}, \tl{mistake}, \&c.; these are called
Inseparable Prepositions.
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../main"
%%% End:
